Predicting the Quality of CDR-H3 Antibody Loop Structural Models

### 2023-03-14 paper.tex
Updates from Overleaf

In order to
determine the most effective feature selection method, the
ML-model was trained on different feature sets selected using manual
selection as well as algorithmic selection strategies (see methods).
None of the
feature selection methods was a best fit for all ML-models. To create a ML-model implementing the encoding and feature selection strategies best suited for the specific \highlight{ML-structure} \lilian{What is this?}, a number of different combinations were tested, summarized in Table~\ref{tab:results_table}. Additional ML-Models were discarded due to poor performance.

\begin{table}
  \centering
  \caption{Summary of Machine-Learning Classifier Performances \lilian{Is this just the top-level classifier? You need something providing this sort of info for the final selection for the binary classifiers. What is multi-/single-layer? What is `First-layer weighted'? Is it needed given that i is always Yes for Multi and No for Single? What is `SVC'? Is `Soft Voting' the same as `Voting(soft)'? What are `Basic' features?}}
  \label{tab:results_tableX}

  \small
  \begin{tabular}{lllllll}\hline
    Features        & Feature       & Parameter         & Multi- / & First-    & Classifier    & MCC  \\
                    & Selection     & Optimization      & Single-  & layer     & Type          &      \\
                    & Method        & Method            & layer    & weighted  &               &      \\ \hline
    Basic           & None          & None              & Single   & No        & SVC           & 0.54 \\
    Basic           & None          & GA$^\dag$         & Single   & No        & SVC           & 0.54 \\
    All             & None          & None              & Single   & No        & Random Forest & 0.58 \\
    Selected        & Random Forest & GA                & Single   & No        & Soft Voting   & 0.59 \\
    Selected        & Random Forest & GA                & Multi    & Yes       & XGBoost       & 0.63 \\
    Selected        & Recursive     & GA                & Multi    & Yes       & XGBoost       & 0.79 \\
                    & Feature       &                   &          &           &               &      \\
                    & Elimination   &                   &          &           &               &      \\
    Selected        & Recursive     & GA                & Multi    & Yes       & Decision-Tree & 0.99 \\
                    & Feature       &                   &          &           &               &      \\
                    & Elimination   &                   &          &           &               &      \\
    Selected-NL$^*$ & Recursive     & GA                & Multi    & Yes       & Voting (soft) & 0.92 \\
                    & Feature       &                   &          &           &               &      \\
                    & Elimination   &                   &          &           &               &      \\ \hline
    \multicolumn{7}{l}{$^*$ No log-file features} \\
    \multicolumn{7}{l}{$^\dag$ Genetic algorithm} \\
    \end{tabular}
\end{table}

>>>>

In order to
determine the most effective feature selection method, the
ML-model was trained on different feature sets selected using manual
selection as well as algorithmic selection strategies (see methods).
None of the
feature selection methods was a best fit for all ML-models. To create a ML-model implementing the encoding and feature selection strategies best suited for the specific types of ML-classifiers selected for the first-layer and top-layer model in combination, a number of different combinations were tested, summarized in Table~\ref{tab:results_table}. Additional ML-Models were discarded due to poor performance.

\begin{table}
  \centering
  \caption{Summary of Machine-Learning Classifier Performances. The classifier type denotes the top-layer classifier. A single-layer model has no binary first layer, only the top-layer classifier. If the first layer is weighted, the binary predictions will carry more weight, the higher their certainty is.  \lilian{Is this just the top-level classifier? You need something providing this sort of info for the final selection for the binary classifiers. What is multi-/single-layer? What is `First-layer weighted'? Is it needed given that i is always Yes for Multi and No for Single? What is `SVC'? Is `Soft Voting' the same as `Voting(soft)'? What are `Basic' features?}}
  \label{tab:results_table}

  \small
  \begin{tabular}{lllllll}\hline
    Features        & Feature       & Parameter         & Multi- / & First-    & Classifier    & MCC  \\
                    & Selection     & Optimization      & Single-  & layer     & Type          &      \\
                    & Method        & Method            & layer    & weighted  &               &      \\ \hline
    Basic           & None          & None              & Single   & No        & SVC           & 0.54 \\
    Basic           & None          & GA$^\dag$         & Single   & No        & SVC           & 0.54 \\
    All             & None          & None              & Single   & No        & Random Forest & 0.58 \\
    Selected        & Random Forest & GA                & Single   & No        & Voting (soft)   & 0.59 \\
    Selected        & Random Forest & GA                & Multi    & Yes       & XGBoost       & 0.63 \\
    Selected        & Recursive     & GA                & Multi    & Yes       & XGBoost       & 0.79 \\
                    & Feature       &                   &          &           &               &      \\
                    & Elimination   &                   &          &           &               &      \\
    Selected        & Recursive     & GA                & Multi    & Yes       & Decision-Tree & 0.99 \\
                    & Feature       &                   &          &           &               &      \\
                    & Elimination   &                   &          &           &               &      \\
    Selected-NL$^*$ & Recursive     & GA                & Multi    & Yes       & Voting (soft) & 0.92 \\
                    & Feature       &                   &          &           &               &      \\
                    & Elimination   &                   &          &           &               &      \\ \hline
    \multicolumn{7}{l}{$^*$ No log-file features} \\
    \multicolumn{7}{l}{$^\dag$ Genetic algorithm} \\
    \end{tabular}
\end{table}
